\Title

### 2024-05-28 source/cadabra/export.tex
Simplified installation, updated hybrid-latex tools
1. Non-trivial refactoring of the build/install scripts.
   This was both to tidy the file structure as well as to simplify the installation
   process. The default install is now as simple as "source SETPATHS; make install".
   Almost all install/build/test/clean actions are now controlled by Makefiles.

2. Updated cdbpreproc.py.
   The Cadabra preprocessor will strip any in-line comments (such as cdb tags) from
   what it thinks are short lines. This failed for some of the examples (some in line
   comments were not deleted). This was fixed

@@

   import cdblib

@@

>>>>

\def\Date{19 Jan 2024}
% \def\FileID{file:}

@@

   Dx{#}::LaTeXForm{"{\Dx}"}.  # LCB: This used to cause a bug, it kills ::KeepWeight for Dx
                               # LCB: But I'm not sure that this is still true.
                               # LCB: So just to be safe I'll leave all Cadabra sources unchanged.
                               # LCB: I can use this trick in this file because it doesn't use ::KeepWeight
   import cdblib

@@

   # gen gamma in terms of partial derivs of Gamma^{a}_{bc}
   tmp = cdblib.get ('gen_gamma_pderiv0','genGamma.export')  # cdb (genGammaPderiv0,tmp)
   tmp = cdblib.get ('gen_gamma_pderiv1','genGamma.export')  # cdb (genGammaPderiv1,tmp)
   tmp = cdblib.get ('gen_gamma_pderiv2','genGamma.export')  # cdb (genGammaPderiv2,tmp)

### 2024-05-28 source/cadabra/genGamma.tex
Simplified installation, updated hybrid-latex tools
1. Non-trivial refactoring of the build/install scripts.
   This was both to tidy the file structure as well as to simplify the installation
   process. The default install is now as simple as "source SETPATHS; make install".
   Almost all install/build/test/clean actions are now controlled by Makefiles.

2. Updated cdbpreproc.py.
   The Cadabra preprocessor will strip any in-line comments (such as cdb tags) from
   what it thinks are short lines. This failed for some of the examples (some in line
   comments were not deleted). This was fixed

@@

@@

>>>>

% =================================================================================================
% compute the first three generalised Gamms (including \Gamma^{a}_{bc})
% this is just provide the LaTeX code for the first three \Gamma's in section 7 of the paper
% these results are never used anywhere else

\begin{cadabra}
   deriv01:=B^{a}:

   deriv02:=-\Gamma^{a}_{b c} B^{b} B^{c}:                # cdb (deriv02.100,deriv02)

   deriv03:=\nabla{@(deriv02)}.                           # cdb (deriv03.100,deriv03)
   distribute     (deriv03)
   product_rule   (deriv03)                               # cdb (deriv03.101,deriv03)
   substitute     (deriv03,$\nabla{B^{a}}->@(deriv02)$)   # cdb (deriv03.102,deriv03)
   substitute     (deriv03,$\nabla{\Gamma^{m}_{s t}}->B^{d}\partial_{d}{\Gamma^{m}_{s t}}$)   # cdb (deriv03.103,deriv03)
   sort_product   (deriv03)                               # cdb (deriv03.104,deriv03)
   rename_dummies (deriv03)                               # cdb (deriv03.105,deriv03)
   canonicalise   (deriv03)                               # cdb (deriv03.106,deriv03)

   deriv04:=\nabla{@(deriv03)}.                           # cdb (deriv04.100,deriv04)
   distribute     (deriv04)
   product_rule   (deriv04)                               # cdb (deriv04.101,deriv04)
   substitute     (deriv04,$\nabla{B^{a}}->@(deriv02)$)   # cdb (deriv04.102,deriv04)
   substitute     (deriv04,$\nabla{\Gamma^{m}_{s t}}->B^{d}\partial_{d}{\Gamma^{m}_{s t}}$)   # cdb (deriv04.103,deriv04)
   substitute     (deriv04,$\nabla{\partial_{e}{\Gamma^{m}_{s t}}}->B^{d}\partial_{d e}{\Gamma^{m}_{s t}}$)   # cdb (deriv04.104,deriv04)
   sort_product   (deriv04)                               # cdb (deriv04.105,deriv04)
   rename_dummies (deriv04)                               # cdb (deriv04.106,deriv04)
   canonicalise   (deriv04)                               # cdb (deriv04.107,deriv04)

   pderiv02 := -@(deriv02).                # cdb (pderiv02.100,pderiv02)
   factor_out (pderiv02, $B^{a?}$)         # cdb (pderiv02.101,pderiv02)
   substitute (pderiv02, $B^{a} -> 1$)     # cdb (pderiv02.102,pderiv02)

   pderiv03 := -@(deriv03).                # cdb (pderiv03.100,pderiv03)
   factor_out (pderiv03, $B^{a?}$)         # cdb (pderiv03.101,pderiv03)
   substitute (pderiv03, $B^{a} -> 1$)     # cdb (pderiv03.102,pderiv03)

   pderiv04 := -@(deriv04).                # cdb (pderiv04.100,pderiv04)
   factor_out (pderiv04, $B^{a?}$)         # cdb (pderiv04.101,pderiv04)
   substitute (pderiv04, $B^{a} -> 1$)     # cdb (pderiv04.102,pderiv04)
\end{cadabra}

% =================================================================================================
\section*{The generalised connection in generic coordinates (for the paper section 7)}

\begin{dgroup*}[spread=5pt]
   \begin{dmath*} {\Gamma}^{a}_{(bc)}(x) = \Cdb*{pderiv02.102} \end{dmath*}
   \begin{dmath*} {\Gamma}^{a}_{(bcd)}(x) = \Cdb*{pderiv03.102} \end{dmath*}
   \begin{dmath*} {\Gamma}^{a}_{(bcde)}(x) = \Cdb*{pderiv04.102} \end{dmath*}
\end{dgroup*}

@@

   # gen gamma in terms of partial derivs of Gamma^{a}_{bc}
   cdblib.put ('gen_gamma_pderiv0',pderiv02,'genGamma.export')
   cdblib.put ('gen_gamma_pderiv1',pderiv03,'genGamma.export')
   cdblib.put ('gen_gamma_pderiv2',pderiv04,'genGamma.export')

@@

   checkpoint.append (pderiv02)
   checkpoint.append (pderiv03)
   checkpoint.append (pderiv04)
\end{cadabra}

### 2024-05-28 source/tex/paper.tex
Minor style changes.
Added a date to each pdf. Reinstated, in Section 7, the equations for the generalised connections in terms of the partial derivatives of the metric connection.

\bgroup
\BegNote{\bf Version 2}
\small%
The first version of this paper was written in 2009. This second version (written in 2019)
differs from the first in a number of important ways. First, the discussion on Cadabra has
been completely rewritten to account for the revised syntax introduced in the latest version
of Cadabra (itself updated in 2016)\footnote{The Cadabra results in this paper are based on
\CdbVersion}. Second, and more importantly, a significant computational error in the first
version (of this paper) has been corrected. Though the algorithms given in the first version
were correct their implementation in Cadabra (by this author) was incorrect. This lead to
errors first in the quartic and higher order terms in the generalised connections and later to computations built upon the generalised connections (e.g., the initial and
boundary value problem and the arc-length equations). The Cadabra codes have been corrected
and thoroughly cross-checked. A number of minor typographical errors have also been
corrected.
% \EndNote
\vskip 2pt

\BegNote{\bf Version 3}
\small%
This version corrects the indicies (and sign) of the left hand side of equations 11.19a-d.
This brings the arXiv version in line with the version on GitHub
\ \url{https://github.com/leo-brewin/riemann-normal-coords}.
% \EndNote
\vskip 2pt

@@

\BegNote{\bf Version 5}
\small%
Versions 2 to 4 used both $Dx^a$ and $\Delta x^a$ to record the change in cooridnates between
two nearby points. This version replaces the $Dx^a$ with $\Delta x^a$.
\EndNote
\egroup

@@

Here are the first three generalised connections
%
%-------------------------------------------------------------------------------
\def\genGammaA{{\Gamma^{a}_{(bc)}(x)}}%
\def\genGammaB{{\Gamma^{a}_{(bcd)}(x)}}%
\def\genGammaC{{\Gamma^{a}_{(bcde)}(x)}}%
\def\genGammaD{{\Gamma^{a}_{(bcdef)}(x)}}%
%-------------------------------------------------------------------------------
%
\begin{dgroup*}[compact,spread={3pt}]
\begin{dmath*}\genGammaA = \cdb{genGamma04}+\BigO{\eps^4}\end{dmath*}%
\begin{dmath*}\genGammaB = \cdb{genGamma14}+\BigO{\eps^4}\end{dmath*}%
\begin{dmath*}\genGammaC = \BigO{\eps^4}\end{dmath*}
\end{dgroup*}
%

>>>>

\bgroup
\BegNote{\bf Version 2}
\small%
The first version of this paper was written in 2009. This second version (written in
2019) differs from the first in a number of important ways. First, the discussion on
Cadabra has been completely rewritten to account for the revised syntax introduced in the
latest version of Cadabra (itself updated in 2016)\footnote{The Cadabra results in this
paper are based on \CdbVersion}. Second, and more importantly, a significant
computational error in the first version (of this paper) has been corrected. Though the
algorithms given in the first version were correct their implementation in Cadabra (by
this author) was incorrect. This lead to errors first in the quartic and higher order
terms in the generalised connections and later to computations built upon the generalised
connections (e.g., the initial and boundary value problem and the arc-length equations).
The Cadabra codes have been corrected and thoroughly cross-checked. A number of minor
typographical errors have also been corrected.
% \EndNote

\vskip 2pt

\BegNote{\bf Version 3}
\small%
This version corrects the indicies (and sign) of the left hand side of equations 11.19a-d.
This brings the arXiv version in line with the version on GitHub
\ \url{https://github.com/leo-brewin/riemann-normal-coords}.
% \EndNote

\vskip 2pt

@@

\BegNote{\bf Version 5}
\small%
Versions 2 to 4 used both $Dx^a$ and $\Delta x^a$ to record the change in cooridnates
between two nearby points. This version replaces the $Dx^a$ with $\Delta x^a$.

\BegNote{\bf Version 6}
\small%
Added back, in section 7, expressions for the generalised connections in terms of the
partial derivatives of the metric connection. These are the same expressions that
appeared in version 1 but were dropped in versions 2-4.
% \EndNote
\egroup

@@

Here are the first three generalised connections in generic coordinates
%
%-------------------------------------------------------------------------------
\def\genGammaA{{\Gamma^{a}_{(bc)}(x)}}%
\def\genGammaB{{\Gamma^{a}_{(bcd)}(x)}}%
\def\genGammaC{{\Gamma^{a}_{(bcde)}(x)}}%
\def\genGammaD{{\Gamma^{a}_{(bcdef)}(x)}}%
%-------------------------------------------------------------------------------
%
\begin{dgroup*}[compact]
\begin{dmath*}\genGammaA = \cdb{genGammaPderiv0}\end{dmath*}%
\begin{dmath*}\genGammaB = \cdb{genGammaPderiv1}\end{dmath*}%
\begin{dmath*}\genGammaC = \cdb{genGammaPderiv2}\end{dmath*}%
\end{dgroup*}
%-------------------------------------------------------------------------------
%
and when the Riemman normal conditions are applied
%
\begin{dgroup*}[compact,spread={3pt}]
\begin{dmath*}\genGammaA = \cdb{genGamma04}+\BigO{\eps^4}\end{dmath*}%
\begin{dmath*}\genGammaB = \cdb{genGamma14}+\BigO{\eps^4}\end{dmath*}%
\begin{dmath*}\genGammaC = \BigO{\eps^4}\end{dmath*}
\end{dgroup*}
%
